Parallel Sorting of Roughly-Sorted Sequences\\CSCI 5172 Fall '16 Project

### 2016-12-06 tex/paper.tex
paper: graphs, outline and additional references

\documentclass[letterpaper, 12pt]{article}
\usepackage[letterpaper]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[doublespacing]{setspace}
\title{Parallel Sorting of Roughly-Sorted Sequences\\CSCI 5172 Fall '16 Project}
\author{Anthony Pfaff, Jason Treadwell}

@@

% TODO: rewrite away the proposal text
Sorting a collection according to some ordering among its items is among the most classic problems of computer science.
A well-established result is the linearithmic  (i.e.\ $O(n \lg n)$) optimal upper bound for sorting sequences of length $n$ by
  comparison.
Commonly-used sorting algorithms such as Mergesort and Quicksort have $\Theta(n \lg n)$ and $\Omega(n \lg n)$ runtimes,
  respectively.

@@

We intend to study and implement sorting of roughly-sorted sequences using both sequential and parallel\cite{altman90} versions
  of the algorithm. In particular, I shall investigate the applicability of the method over very large sequences,
  accelerated using graphics hardware. A GPU is dedicated graphics hardware that also excels at performing frequent, basic
  computations over large amounts of data. The use of GPUs for numerical applications is a recent and rapidly-growing development
  in computer science and software engineering. Suitable hardware is now commonly available in consumer devices and may herald a
  paradigm shift in how we efficiently perform common and indispensable tasks like sorting.

I propose to develop implementations of the method using C and Nvidia's CUDA framework, comparing the results with sequential
  implementations running on both the GPU and CPU as well as with the classic Mergesort and Quicksort algorithms. If time
  permits, I would also like to compare the method to parallel versions of the latter two algorithms.

\bibliographystyle{plain}
\nocite{*}
\bibliography{refs} % bib database

>>>>

\documentclass[letterpaper, 12pt]{article}
\usepackage[letterpaper]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[doublespacing]{setspace}
\usepackage{url, rotating, sectsty}

\sectionfont{\fontsize{12}{15}\selectfont}

\title{Parallel Sorting of Roughly-Sorted Sequences\\CSCI 5172 Fall '16 Project}
\author{Anthony Pfaff, Jason Treadwell}

@@

\section{The Array Sorting Problem}

Sorting a collection according to some ordering among its items is among the most classic problems of computer science.
A well-established result is the linearithmic  (i.e.\ $O(n \lg n)$) optimal upper bound for sorting sequences of length $n$ by
  comparison.

\section{Sorting Roughly-Sorted Sequences}

@@

\section{Sequential Implementation}

\section{Sorting Arrays in Parallel}

\section{Parallel Radius Determination}

\section{Parallel Roughsort Implementation}

\section{Experimental Results}

\begin{sidewaysfigure}
\input{plots/k2}
\vspace{-4ex}
\caption{\label{fig:k2}{\em
  Sort Runtimes over Arrays of Length $n\cdot 10^6$, $k = 2$
}}
\end{sidewaysfigure}

\begin{sidewaysfigure}
\input{plots/k15}
\vspace{-4ex}
\caption{\label{fig:k15}{\em
  Sort Runtimes over Arrays of Length $n\cdot 10^6$, $k = 15$
}}
\end{sidewaysfigure}

\begin{sidewaysfigure}
\input{plots/n750k}
\vspace{-4ex}
\caption{\label{fig:n750k}{\em
  Sort Runtimes over Arrays of Radius $k$, $n = 0.75\cdot 10^6$
}}
\end{sidewaysfigure}

\begin{sidewaysfigure}
\input{plots/n1250k}
\vspace{-4ex}
\caption{\label{fig:n1250k}{\em
  Sort Runtimes over Arrays of Radius $k$, $n = 1.25\cdot 10^6$
}}
\end{sidewaysfigure}

\clearpage
\section{Explanation of Results}

\section{Conclusion}

\clearpage
\bibliographystyle{plain}
\nocite{*}
\bibliography{refs} % bib database
